The SMT Competition 2015--2018

### 2019-08-16 2018/report/SMT-COMP.tex
figures -> numbers
reproducibility -> replicability; minor other changes

The use of StarExec ensures the \emph{reproducibility} of the competition. The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition e.g. all benchmarks and copies of all tools. In addition, a GitHub organisation (\url{https://github.com/SMT-COMP/smt-comp}) has been setup to archive previous results and store the tools used by organisers to run the competition.

@@

Table~\ref{table:participation-by-track} summarizes these figures and
shows how many solver versions were submitted to each track of the
competition.  Note that solver versions may be entered into multiple
tracks.  Therefore, the total number of solver versions for each year
is typically less than the sum over all tracks.

>>>>

The use of StarExec ensures the \emph{replicability} of the competition. The publicly accessible space \url{https://www.starexec.org/starexec/secure/explore/spaces.jsp?id=2641} stores all of the information required to rerun the competition, e.g., all benchmarks and copies of all tools. In addition, a GitHub organization (\url{https://github.com/SMT-COMP/smt-comp}) has been set up to archive previous results and store the tools used by organizers to run the competition.

@@

Table~\ref{table:participation-by-track} summarizes these numbers and
shows how many solver versions were submitted to each track of the
competition.  Note that solver versions may be entered into multiple
tracks.  Therefore, the total number of solver versions for each year
is typically less than the sum over all tracks.
